### 2021-02-05 README.Rmd
Add actions

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/zonebuilders/zonebuilder.svg?branch=master)](https://travis-ci.org/zonebuilders/zonebuilder)
<!-- badges: end -->

>>>>

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/zonebuilders/zonebuilder.svg?branch=master)](https://travis-ci.org/zonebuilders/zonebuilder)
[![Codecov test coverage](https://codecov.io/gh/zonebuilders/zonebuilder/branch/master/graph/badge.svg)](https://codecov.io/gh/zonebuilders/zonebuilder?branch=master)
[![R-CMD-check](https://github.com/zonebuilders/zonebuilder/workflows/R-CMD-check/badge.svg)](https://github.com/zonebuilders/zonebuilder/actions)
<!-- badges: end -->
